Fractional Types

### 2016-12-18 typespp.tex

Our constructions of $\order{p}$ and $\iorder{p}$ are instances of a general pattern that we have instantiated to the setting of $\Pi$ and adapted to explicitly refer to weak (i.e., up to $\isotwo$ in our case) equivalences. In the general construction~\cite{looping}, a group $G$ is known to induce two groupoids, a looping groupoid $LG$ and a delooping groupoid $BG$. These are defined as follows.

The looping groupoid $LG$ has the group elements as objects and, for every
group elements~$g$ and $h$, there is a morphism between $g$ and $h^{-1} \cdot g
\cdot h$. If we fix a type $\tau$ and a particular 1-combinator $p : \tau \iso
\tau$, we get a group whose elements are the iterates $p^k$. The corresponding
looping groupoid would have all the iterates as objects and morphisms between
$p^{k_1}$ and $p^{k_2}$ whenever there exists an integer $j$ such that
$p^{k_2}$ is equivalent to $p^{-j} \odot p^{k_1} \odot p^{j}$. By
Lem.~\ref{lem:distiterplus}, the latter term is $\isotwo$-equivalent to
$p^{-j+k_1+j}$ which is $\isotwo$-equivalent to $p^{k_1}$. In other words, we
have a morphism between $p^{k_1}$ and $p^{k_2}$ whenever they are
$\isotwo$-equivalent which is consistent with our definition of iteration
groupoids. The delooping groupoid $BG$ has one trivial element and for each
group element $g$ a morphism from that element to itself. Modulo
$\isotwo$-equivalences, this is consistent with our definition of symmetry
groupoids.

>>>>

Our constructions of $\order{p}$ and $\iorder{p}$ are instances of a general
pattern that we have instantiated to the setting of $\Pi$ and adapted to
explicitly refer to weak (i.e., up to $\isotwo$ in our case) equivalences. In
the general construction~\cite{looping}, a group $G$ is known to induce two
groupoids, a looping groupoid $\looping{G}$ and a delooping groupoid
$\delooping{G}$. These are defined as follows.

The looping groupoid $LG$ has the group elements as objects and, for every
group elements~$g$ and $h$, there is a morphism between $g$ and $h^{-1} \cdot g
\cdot h$. If we fix a type $\tau$ and a particular 1-combinator $p : \tau \iso
\tau$, we get a group whose elements are the iterates $p^k$. The corresponding
looping groupoid would have all the iterates as objects and morphisms between
$p^{k_1}$ and $p^{k_2}$ whenever there exists an integer $j$ such that
$p^{k_2}$ is equivalent to $p^{-j} \odot p^{k_1} \odot p^{j}$. By
Lem.~\ref{lem:distiterplus}, the latter term is $\isotwo$-equivalent to
$p^{-j+k_1+j}$ which is $\isotwo$-equivalent to $p^{k_1}$. In other words, we
have a morphism between $p^{k_1}$ and $p^{k_2}$ whenever they are
$\isotwo$-equivalent which is consistent with our definition of iteration
groupoids.
